%preamble
\documentclass{article}
\synctex=1

%title page
\title{Skyfall movie notes}

\author{Arun Woosaree}

%actual document
\begin{document}
  \maketitle %insert titlepage here

  \section{March 14}
  \subsection{Premovie notes}
  \textbf{Technology in Society}
    Old ways vs new ways
  \begin{itemize}
    \item Q - engineer who makes tech for Bond, gadgets like:
            \begin{itemize}
              \item transportation
              \item weapons
              \item communication
            \end{itemize}
  \end{itemize}

  \subsection{Movie begins}
  Movie begins wih bond walking in a hallway holding a gun.
  He wants to help a man bleeding to his death ut over the phone, a female talls him
  to leave the man alone because there isn't time

  Car chase, crash and shootout in some foreign bazaar. Bond if after some guy
  and british hq says they cannot affford to lose some list. Bike chase on rooftops
  around the bazaar. They're now on a train. (bond and te guy running away). The black woman has to follow
  by car. He gains control of a caterpillar vehicle on the train, escapee shoots the link of the traincar,
  so bond digs caterpillar arm in the passeger car and continues pursuit. Fist fight on top of trin after tunnel.

  Blakc woman waits with sniper as train comes out of tunnel, she cannot get a clear shot at Bond, and
  british governmnent (white old lady) pressures her, and she accidentally hits bond, and bond falls off the train into the water
  and the enemy gets away.

  Bond washes away on river and adele's song plays.

  \noindent\rule{\textwidth}{1pt}
  Title sequence\\
  \noindent\rule{\textwidth}{1pt}

  setting: london, mi6, British lady reviewing Bond's Obituary, or ather she's writing it.
  Next day, we find out they lost a computer drive had a list of all the nato agents with links to
  some link to terrorist organizations, the chase scene with Bond happened 3 month ago.
  They get a call that someone is trying to decrypt the hard drive, and the person is in london, uk.
The signal is coming from mi6, behind their own firewall, from the british lady's computer.
The message says "Thhink on your sins" when they try to remotely shut it down.
Explosion in mi6 hq.

Bond is an animal at drinking, and takes another drink in the morning right after
the night of partying hard.
Bond meets the british lady, and they exchange in salty but matter of fact style conversation
So, bond is back in mi6.

There's a rat in the mi6, and they need to find him.
Bond does some tests for his health, while he gets breifed.
He fails his shooting target practice miserably
He is super out of it for his mental/ psychological evaluation
He is still obviously very worn out, from well, being shot and left for dead.
He removes the bullet by himself with a knife.
And he hands it over to be analyzed.
  Technology:
  \begin{itemize}
    \item From a computer in the suitcase, they receive a signal from the hard drive that it'd being decrypted
    and they're able to remotely track where it is

  \end{itemize}

  \section{March 16}
    There's a new Q, this one is a younger scientist\\
    Bond has been reassigned - temporary suspension from field work.
    He talked to black woman who shot him, and they have a lighthearted conversation.
    Bond has pased all his tests and is now an agent again.
    He gets asked why not play dead, and why he decided to join mi6 again.
    Depleted uranium shell (bullet) is what hit him. (The one he sent in for analysis
    and dg out with a knife). He gets a new mission, having to do with getting information
    on the list. British woman tells bond that he's ready for this. Also when bond leaves,
    she reveals that he didn't pass the tests.

    Bond meets young agent in an art museum. He is bond's new quartermaster. (Q)
    Bond does not appove of Q's young age. He is a hacker type person.
    Q hands a passport and a fingerprint locked gu. A radio transmitter that broadcasts
    his location (Distress signal). He doesn't get an exploding pen, and Q asks
    hm to return the equipment in one piece

    \textbf{Technology:}
    \begin{itemize}
      \item Fingerprint locked gun (only bond can fire it)
      \item Radio distress signal broadcaster
    \end{itemize}

    Bond is off to Shanghai. As he approaches building, he sees a guy being shot.
    Bond exits his car and goes in the building to follow the murderer, with his gun drawn.
    The man shot was a police officer. Bond puts his gun away, and jumps to hold onto elevator,
    from underneath. Man in elevator hears bond hanging below and draws his gun.
    He exits elevator and bond climbs up. Room has a lot of glass. Bond walks stealthily around
    and the man he's after is unlocking some brfiefcase and breaking into something by cutting glass
    or using a computer or something
    . Music builds up.
    Man readies some assult rifle looking thing, bond still approaches.
    Yes he was cutting a hole in the glass.
    The man looks like he is an asssassin, and the hole was for him to
    snipe someone
    Bond engages after the sniper shot has been fired. This is a man on man fight.
    He asks the assassin who has the list as he's hanging off the side of the building.
    The assassing chooses to let go and suicide, and bond makes eye contact with the woman in
    the other building across where a guy was shot. Bond picked up some token and looks at it.

    Scene london:
    British woman's computer is hacked while she's at home, and the hacker
    shows the first 5 names of the agents leaked online (youtube) and then leaves
    the message "Think on your sins" for the british woman to think about.
    The person who stole the list has successfully decrypted the files

    Bond again, and he's in some room, person knocks on door, bond draws gun, but it turns out
    to be the black woman. They talk again, and bond is mocked for shaving the old fashioned way.
    (The super sharp barber knife) And then he asks the black woman to help him out.
    She jokingly says something along the lines of "you're puttin g your lie in my hands again"
    "old dog, new tricks"

    Bond goes to some private event, at a csino. Bond cashes in the token he found from the
    assassin. Bond makes eye contact with same woman he saw in the other building.
    Bond gets a suitcase of a hella lot of money from that one token
    it must be special. The woman he made eye contact with approaches bond,
    and asks him for a drink. They go for a drink, and the woman asks if she can ask
    a "buisiness question that has to do with death". She asks why he killed batrise or something like that.
    Bond replies I wan to be your employer if I heard that correctly. She excuses herself,
    but bond stops her and observes that she has 3 bodyguards and that she is "being controlled" not being protected,
    and also notices some mark on her hand.
    Bond wants to save her. She says "when I leave they are going to kill you."
    if you survive, she will take bond to their leader. (They want to kill him because they don't
    want him leaving with the suitcase of money)

    end: time: 1:03:53

    \section{March 19}
    In context of exam here's what we need to know about the impact of technology on society,
    technological improvements that make life better
    \begin{itemize}
      \item old:
        \begin{enumerate}
          \item cut throat with razor
          \item every now and then, a trigger is pulled
        \end{enumerate}
      \item new ways
        \begin{enumerate}
          \item Q- "we don't go in for that anymore (exploding pen gadgets)"
          \item computing
          \item language
          \item Q says he can do a lot more damage sitting in his pajamas in the morning by hacking with a computer
        \end{enumerate}
    \end{itemize}

    Bond insists to try to help her. She asks if bond can kill him. And bond accepts the challenge.
    Bond gets surrounded when he atempts to leave the casino. They fist fight and fall into a pit with an alligator.
    Bond is at gun point, but it's his fingerprint locked gun, and the alligator eats the guard.
    Bond then steps on an alligator and escapes.

    Bond meets the woman in her hotel room, and they shower together and kiss.

    Setting: London, british woman watching news. Mi6 agents whose names were leaked are getting killed
    in whatever middle east country.

    Setting: bond in on a boat in the middle of nowhere with the woman, and they approach land. Looks like they are going to get dumped off the boat, because there are many
    men holdin guns  behind them. The go in the land in a trashed place. The place was abandoned because
    someone did damage with a computer. Bond is locked in a room tied to a chair, surrounded by a bunch of computer
    hardware. A man approaches him who knows his name. The man tells a story of rats, and how
    if yu leave them alone without food, they eat each toher until there's 2 left. He says him and bond are the last 2 rats. The man appears salty because
    he was te british woman's favourite. He shows bond that he failed all his tests. (Because he hacked into mi6 so he has access for this)
    He unbuttons bond's shirt to look at his bullet wound.

    (The man's name is Silva)
    He unties bond's hands, mocks england. (There are guards behind bond). He mocks the gadgets, and he tries to tempt bond,
    saying he can do any secret mission, Modifying stocks, rigging elections (uganda) for the highest bidder, screwing with
    communications (spy) sattelites, bond mentions gas explosion in london. Silva says bond can be his own boss. They walk around the island. Bond finds he woman, who looks like she was beat becuse there's dry
    blood on her mouth it seems. Bond takes a shot of whiskey. The man force kisses her, places a shot of whiskey on her head, and
    tells bond to shoot the shot glass on her head. His hand does not seem steady.  (he has to because there is a guard holding a gun to bond's head).
    Bond successfully does it but the man takes another shot and kills the lady. He gets mad, and says it's a waste of good scotch.
    A bunch of helicopters go to the island, because bond activated his radio distress signal, which worked despite
    all the other new technology, Silva probably didn't think to use a radio jammer.

    They have silva trapped in a glass room. Brtish woman talks to him. They have his name on a memorial
    wall in the building he attacked, but his past will be erased.

    Q analyzes Silvia's computer. He mentions that it has a failsafe to wipe the computer if someone tries to access it.
    The code changed itself when Q tries to access it. Bond notices Grandborough, which then reveals that it's a map.
    Silvia hacked into the computers though because Q plugged in the computer directly when he was trying to hack Silvia's

    Q then tracks Bond's location underground. It is revealed that Silvia had all this planned. He planned to get
    captured, then escape. There's a train coming to bond as he ties to access a closed door. He ends up shooting the door
    to get in. Bind has to get on the train as it's moving. Silvia is disguised as a policeman. Q tries to figure out where
    Silvia is going using all this technology but bond just looks at the metro line map.


    \textbf{March 21}
    On foot chase, bond is in train. Bond figures out that Silvia is going for (Tanna?)
    (The british woman in charge of bond and at one point, Silvia.) He figures this out
    by looking at the map, while Q stares a tthe computer screens at heaquarters.
    Bond catches up to Silvia, and he explodes part of the metro line, which
    definitely was in antipation of bond being right there and then. Silvia get closer
    to the court hearing, where mi6 is being asked by the public if they are even relevant
    Silvia breaks in ans shoots anyone near the british lady, and then bond comes in,
    shoots fireextinguishers, to fog up the room and goes after silvia. Silvia escapes in a
    police car.

    Bond switches car, as he goes off with the british woman. they
    want to leave a trail that only Silvia can follow. Bond switches to
    an older car, one with all of the fancy gadgets, like with a seat ejector.
    Q gets caught doin the unofficial stuff but his manager tells him to carry on
    helping bond.

    Bond and the british lady go to a deserted mountainous region where bond was raised.
    He did say earlier he's "going back in time". The place is called Skyfall.
    They go to his hold house in the middle of nowhere. The ritish lady is to be used
    as bait.

    Old man comes out of nowhere with huting rifle. Turns out it's the man that raised bond.
    Kinkay. They don't have many munitions, only a few hunting rifles but Kinkay says that sometimes the old
    ways are the best, and takes out a knife.
    British lady gets to work rigging dynamite traps in the house.
    They wait for Silvia to come.

    scotland

    They arrive, with like 15 men all armed with assault rifles. They start breaking into the house,
    but bond is waiting in the  car, and uses the hidden guns in the headlights to eliminate half of the men.
    Bond realizes Silvia is not there. Silvia arrives in a helicopter once all the men
    are down. Helicopter unleashes turret on house. Bond tells Kinkay and british lady to use
    tunnel in house to escape. Silvia walke out of helicopter with like 15 more men.
    Silvia throws granades into house. Bond takes propane tank away from kitchen as Silvia throws grenade.
    Bond realizen they destroyed his beloved car. (It exploded) He gets mad and sets up trap with the propane tanks. He then runs in the tunnel.
    Shit explodes, and hits the helicopter, and the helicopter crashes into the house.
    Tunnel lights up with fire. Due to the massive explosion, Kinkay and british lady assume bond is dead.
    Silvia is confused, until he sees a flashlight in the distance. Silvia approches her, while he tells men to
    make sure bond is dead. Bond comes out of tunnel, and sees man with gun, jumps him. Silvia finds him running in
    open field, and has gun pointed to him. But the ground below them is wek so bond gets guy to shoot hole below them,
    and they fall into a sort of lake. (Reminds me of yellowstone, but then wouldn't the water be hot af.)
    Silvia is surprised and bummed out lol. He goes to the other house where Kinkay and british lady are hiding. (In a church)
    He meets british woman, and hold her bloody hand.

    \textbf{March 23}
    Silvia holds gun to british lady in church. He says free both of us with the same bullet.
    Only you can do it. Then bond throws a knife before that happens into silvia's back.
    He's visibly upset. (silvia). Silvia falls to the ground. British lady dies in dignity in Bond's arms.

    Setting: day in london, bond stands on top of tower in london, and talks with black woman.
    She gives a box which the british woman left for bond, a ceramic british bulldog.
    Black woman's name is Eve.

\end{document}
